### 2017-12-20 master/paper.tex
Add publication list

>>>>

%Publication List
\chapter*{Publication List}
\addcontentsline{toc}{chapter}{Published List}
\section*{Journal}
\begin{enumerate}[{[}1{]}]
\item
    Takuro Yamamoto, Takuma Hara, Takuya Ishikawa, Hiroshi Oyama, Hiroaki Takada, and Takuya Azumi,
    ``Component-Based mruby Platform for IoT Devices,"
    \emph{IPSJ Journal of Information Processing},
    2017 (submitted).
\item
    Takuro Yamamoto, Hiroshi Oyama, and Takuya Azumi,
    ``Component-Based Framework of Lightweight Ruby for Efficient Embedded Software Development,''
    \emph{JSSST Journal on Computer Software},
    vol. 34, no. 4, pp. 3-16, 2017.
\end{enumerate}

\section*{International Conference}
\begin{enumerate}[{[}1{]}]
\item
    Takuro Yamamoto, Takuma Hara, Takuya Ishikawa, Hiroshi Oyama, Hiroaki Takada and Takuya Azumi,
    ``TINET+TECS: Component-Based TCP/IP Protocol Stack for Embedded Systems,''
    \emph{In Proceedings of the IEEE 14th International Conference on Embedded Software and Systems (ICESS)},
    2017.
\item
    Takuro Yamamoto, Hiroshi Oyama, and Takuya Azumi,
    ``Lightweight Ruby Framework for Improving Embedded Software Efficiency,''
    \emph{In Proceedings of the 4th IEEE International Conference on Cyber-Physical Systems, Networks, and Applications (CPSNA)},
    pp. 71-76, 2016.
\end{enumerate}
